\Title

### 2023-02-20 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

To transform each movie into events as the ones recorded by a DVS, we compute a gradient image (initialized at zero) by adding the gradient of the pixels' intensity over two successive frames. For a specific pixel and timestamp, an event is generated if the absolute value of this gradient exceeds a threshold. The event has either an OFF or ON polarity respectively, whether the gradient is negative or positive. This signed threshold value is then subtracted from the residual gradient image. When applied to the whole movie, the event stream is similar to the output of a neuromorphic camera~\citep{rasetto_challenges_2022}, that is, a list of events defined by $x_\arank$ and $y_\arank$ (their position on the pixel grid), their polarity $\polev_\arank$ (ON or OFF) and time $\timev_\arank$  (\seeFig{motion_task}-\textit{(Right)}). The goal here is to infer the correct motion solely by observing these events. 
% \note{ the task is full-field rigid translations, the model resolves it locally (analogy to the input from V1 to MT) }
%%%-----------------------------------------------------------------
\subsection{The Heterogeneous Delays SNN (HD-SNN) model}
%----------------------------%
%
\begin{figure}%[t!]
    \centering
    \includegraphics[width=0.980\linewidth]{figures/HDSNN_graph.pdf}
  \caption{\textbf{Core mechanism of the HD-SNN model.} \textit{(Top-Left)}~Two spiking motifs are emitted by four presynaptic neurons. Once integrated by the synapses of the postsynaptic neuron~\textit{(Right)}, the spiking motifs are shifted in time by the synaptic delays and weighted by the synaptic weights~\textit{(Middle-Left)}. When they reach the soma of the postsynaptic neuron, the different spikes contribute to a modification of its membrane potential according to an activation function. In this example, we use the same activation function as a Leaky Integrate and Fire neuron~\textit{(Bottom-Left)}. The first spiking motif is synchronized by the synaptic delays and leads to a sudden increase of the membrane potential of the postsynaptic neuron. An output spike is emitted when reaching the threshold. 
  \textit{(Right)}~An illustration of a spiking neuron with different synaptic weights (represented by the thickness of the synapses) and different synaptic delays (represented by the length of the synapses). }%
    \label{fig:izhikevich}%
\end{figure}%
% 
%----------------------------%
In a neurobiological recording or in the sensory signal obtained from an event-based camera, the input consists of a stream of \emph{spikes} or \emph{events}. This can be formalized as a list of neural addresses and timestamps tuples $\event = \{(\presynaddr_\arank, \timev_\arank)\}_{\arank \in [1,\numevent]}$ where $\numevent \in \mathbb{N} $ is the total number of events in the data stream and the rank $\arank$ is the index of each event in the list of events (\seeFig{izhikevich}-\textit{(Top-Left} for an illustration). Events are typically ordered by their time of occurrence. Each event has a time of occurrence $\timev_\arank$ and an associated address $\presynaddr_\arank$. This defines an address space $\presynaddrspace$ which consists of the set of possible addresses. In a neurobiological recording, this can be the identified set of presynaptic neurons. For neuromorphic hardware, this can be defined as $[1, \Npol] \times [1, \Nx]\times[1, \Ny] \subset \mathbb{N}^3$ where $\Npol$ is the number of polarities ($\Npol=2$ for the ON and OFF polarities coded in event-based cameras) and $(\Nx, \Ny)$ is the height and width of the image in pixels. As such, an address $\presynaddr_\arank$ is typically in the form $(\polev_\arank, x_\arank, y_\arank)$ for event-based cameras.

>>>>

To transform each movie into events as the ones recorded by a DVS, we compute a gradient image (initialized at zero) by computing the temporal gradient of the pixels' intensity over two successive frames. For a specific pixel and timestamp, an event is generated if the absolute value of this gradient exceeds a threshold. The event has either an OFF or ON polarity respectively, whether the gradient is negative or positive. This signed threshold value is then subtracted from the residual gradient image. When applied to the whole movie, the event stream is similar to the output of a neuromorphic camera~\citep{rasetto_challenges_2022}, that is, a list of events defined by $x_\arank$ and $y_\arank$ (their position on the pixel grid), their polarity $\polev_\arank$ (ON or OFF) and time $\timev_\arank$  (\seeFig{motion_task}-\textit{(Right)}). The goal here is to infer the correct motion solely by observing these events. 
% \note{ the task is full-field rigid translations, the model resolves it locally (analogy to the input from V1 to MT) }
%%%-----------------------------------------------------------------
\subsection{The Heterogeneous Delays SNN (HD-SNN) model}
%----------------------------%
%
\begin{figure}%[t!]
    \centering
    \includegraphics[width=0.980\linewidth]{figures/HDSNN_graph.pdf}
    \caption{\textbf{Core mechanism of the HD-SNN model.} \textit{(Top-Left)}~Two spiking motifs are emitted by four presynaptic neurons. Once integrated by the synapses of the postsynaptic neuron~\textit{(Right)}, the spiking motifs are shifted in time by the synaptic delays and weighted by the synaptic weights~\textit{(Middle-Left)}. When they reach the soma of the postsynaptic neuron, the different spikes contribute to a modification of its membrane potential according to an activation function. In this example, we use the same activation function as a Leaky Integrate and Fire neuron~\textit{(Bottom-Left)}. The first spiking motif is synchronized by the synaptic delays and leads to a sudden increase of the membrane potential of the postsynaptic neuron. An output spike is emitted when the membrane potential reaches the threshold, and it is then resetted.   \textit{(Right)}~An illustration of a spiking neuron with different synaptic weights (represented by the thickness of the synapses) and different synaptic delays (represented by the length of the synapses). }%
    \label{fig:izhikevich}%
\end{figure}%
% 
%----------------------------%
In a neurobiological recording or in the sensory signal obtained from an event-based camera, the input consists of a stream of \emph{spikes} or \emph{events}. This can be formalized as a list of neural addresses and timestamps tuples $\event = \{(\presynaddr_\arank, \timev_\arank)\}_{\arank \in [1,\numevent]}$ where $\numevent \in \mathbb{N} $ is the total number of events in the data stream and the rank $\arank$ is the index of each event in the list of events (\seeFig{izhikevich}-\textit{(Top-Left} for an illustration). Events are typically ordered by their time of occurrence. Each event has a time of occurrence $\timev_\arank$ and an associated address $\presynaddr_\arank$. This defines an address space $\presynaddrspace$ which consists of the set of possible addresses. In a neurobiological recording, this can be the identified set of presynaptic neurons. For neuromorphic hardware, this can be defined as $[1, \Npol] \times [1, \Nx]\times[1, \Ny] \subset \mathbb{N}^3$ where $\Npol$ is the number of polarities ($\Npol=2$ for the ON and OFF polarities coded in event-based cameras) and $(\Nx, \Ny)$ is the height and width of the image in pixels. As such, an address $\presynaddr_\arank$ is typically in the form $(\polev_\arank, x_\arank, y_\arank)$ for event-based cameras.
